Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-09-14 doc/tfp_2011_final/main.tex
for the final version

The iTask system~\cite{iTask} is a library for the functional language
`Clean' targeted at distributed workflow management. The library
provides a set of combinator functions (some of which perform map/fold
operations) that facilitate applications running in different nodes
of a distributed system to communicate, exchange information and
coordinate their computations.

@@

\paragraph{Acknowledgements.}
The authors are grateful to the ProVal team for support and comments
on early versions of the library and of this paper.

@@

% LocalWords:  parallelize functor parameterized indices endianness monomorphic
% LocalWords:  genericity executables OCamlMPI MapReduce marshalling functors

>>>>

The iTask system~\cite{iTask} is a library for the functional language
`Clean' targeted at distributed workflow management. The library
provides a set of combinators (some of which perform map/fold
operations) that facilitate applications running in different nodes
of a distributed system to communicate, exchange information and
coordinate their computations.

@@

\paragraph{Acknowledgments.}
The authors are grateful to the ProVal team for support and comments
on early versions of the library and of this paper.

@@

% LocalWords:  parallelize functor parameterized indices endianness monomorphic
% LocalWords:  genericity executables OCamlMPI MapReduce marshalling functors
% LocalWords:  workflow combinators granularities
